The Bolocam Galactic Plane Survey: Survey Description and Data Reduction

### 2009-04-20 methods/ms.tex
some more fixes

Submillimeter observations of Galactic sources have been conducted by
a variety of different groups focusing on small regions since
bolometer technology was developed.  The Submillimeter Common-User
Bolometer Array (SCUBA) on the 15-m James Clerk Maxwell Telescope
mapped many significant regions in the galactic plane over its 8 year
lifetime \citep{holland99,difrancesco08}, but never completed a
contiguous survey of the galactic plane.  The Bolocam instrument has been
used on the 10.4-m Caltech Submiliimeter Observatory (CSO) to map nearby large
molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
MAMBO on the 30-m IRAM telescope has been used at 1.2 mm to map
more distant regions of more massive star formation \citep{motte07}.
None of these surveys covered a significant fraction of the Galactic plane.

@@

% Figure 3
\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright molecular
emission lines are shown at their rest frequencies.  Note that the Bolocam
passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
measurements largely uncontaminated.  SO and CH$_3$OH lines are probably the
dominant contributors to line flux in the passband.  \citet{nummelin1998} found
that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
and \citet{yoshida2005} reported $>40\%$ in Orion A from line emission over the
260-328 GHz band. Other lines lying in the Bolocam passband include CS($5\to4$)
and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
GHz).  A follow-up project will attempt to determine the contribution of lines
to the BGPS flux density measurements.}
{fig:Bandpass}{1.0}

@@

The Bolocam observations are sensitive to structure between 35\arcsec\ and
about 200\arcsec\ (half the array field of view, see figure
\ref{fig:PCA_filter}).  An indicative analysis of the spatial filter function
of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
of the filter function in our survey in figure \ref{fig:PCA_filter}.  The data were
sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
using observations of Mars, Uranus, and Neptune, and they are accurate to
$\sim$20\%.  The flux calibration is described in section \ref{sec:FluxCalibration}.

@@

The BGPS maps are the convolution of the (nearly Gaussian)
primary beam $G(\xad)$ and an effective high-pass
spatial filter $F(\xad)$ (figure \ref{fig:PCA_filter}),
\[
M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
\]

@@

\bf{Claudia suggested that this section be removed or changed to an `advertisement' section
where we indicate what follow-up work needs to be done - seems reasonable, since this
is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}

>>>>

Submillimeter observations of Galactic sources have been conducted by
a variety of different groups focusing on small regions since
bolometer technology was developed.  The Submillimeter Common-User
Bolometer Array (SCUBA) on the 15-m James Clerk Maxwell Telescope
mapped many significant regions in the galactic plane over its 8 year
lifetime \citep{holland99,difrancesco08}, but never completed a
contiguous survey of the galactic plane.  The Bolocam instrument has been
used on the 10.4-m Caltech Submillimeter Observatory (CSO) to map nearby large
molecular clouds at 1.1 mm and identify hundreds of cores \citep{enoch06}.
MAMBO on the 30-m IRAM telescope has been used at 1.2 mm to map
more distant regions of more massive star formation \citep{motte07}.
None of these surveys covered a significant fraction of the Galactic plane.

@@

% Figure 3
\Figure{bolocam_bandpass}{The Bolocam 1.1 mm bandpass.  Bright molecular
emission lines are shown at their rest frequencies.  Note that the Bolocam
passband rejects $>90\%$ of the $^{12}$CO flux, leaving our continuum
measurements largely uncontaminated.  SO$_2$ and CH$_3$OH lines are likely 
strong contributors to line flux in the passband.  \citet{nummelin1998} found
that 22\% of the flux density in one pointing towards Sgr B2 was from lines,
and \citet{yoshida2005} reported $>40\%$ in Orion A from line emission over the
260-328 GHz band. Other lines lying in the Bolocam passband include CS($5\to4$)
and ($6\to5$) (245 and 293 GHz), HCN($3\to2$) (265 GHz) and HCO$^+(3\to2)$ (267
GHz).  } 
% A follow-up project will attempt to determine the contribution of lines
% to the BGPS flux density measurements.}
{fig:Bandpass}{1.0}

@@

The Bolocam observations are sensitive to structure between 35\arcsec\ and
about 200\arcsec\ (half the array field of view, see figure
\ref{fig:PCA_Filter}).  An indicative analysis of the spatial filter function
of the iterative mapping scheme is given in \citet{enoch06}, and we present a detailed analysis
of the filter function in our survey in figure \ref{fig:PCA_Filter}.  The data were
sampled onto a uniform 7\farcs2 grid.  Flux density calibrations were performed
using observations of Mars, Uranus, and Neptune, and they are accurate to
$\sim$20\%.  The flux calibration is described in section \ref{sec:FluxCalibration}.

@@

The BGPS maps are the convolution of the (nearly Gaussian)
primary beam $G(\xad)$ and an effective high-pass
spatial filter $F(\xad)$ (figure \ref{fig:PCA_Filter}),
\[
M'(\xad) = (G(\xad) \otimes F(\xad)) \otimes M(\xad)
\]

@@

{\bf Claudia suggested that this section be removed or changed to an `advertisement' section
where we indicate what follow-up work needs to be done - seems reasonable, since this
is mostly junk pilfered from the `letter'.  However, we need to keep the last sentence around...}

TEST: \ref{fig:BGPSMontage}
